Knowledge Representation for Service Robots: Supply and Demand

### 2012-05-13 krs-survey.tex
Started to fill section on 'Modality' (was Possible Worlds)

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf B. Representation}
            child {node [taxon] {{\bf B.5}. Memory}}
            child {node [taxon] {{\bf B.4}. Introspection}}
            child {node [taxon] {{\bf B.3}. Possible Worlds}}
            child {node [taxon] {{\bf B.2}. Context}}
            child {node [taxon] {{\bf B.1}. Roles}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\subsubsection{Possible-Worlds and representing what others know}
\label{sect|possible-worlds}

Linked to the context representation, but seen from another angle, knowledge
representation systems may provide explicit ways to model other point of view
on the world. This ability is often referred as the \emph{perspective taking}
ability.

\cite{Levesque2008}, p. 4

@@

Since McCarthy's \emph{Situation Calculus} in 1963, numerous knowledge
representation formalisms dedicated to representation and reasoning about
actions and situation have emerged: besides situation calculs, \emph{fluent
calculus} and \emph{event calculus} are the main ones.
Thielscher~\cite{Thielscher2011}} recently proposed a unification of these
approach in a new \emph{action calculus}.

>>>>

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf B. Representation}
            child {node [taxon] {{\bf B.5}. Memory}}
            child {node [taxon] {{\bf B.4}. Introspection}}
            child {node [taxon] {{\bf B.3}. Modality}}
            child {node [taxon] {{\bf B.2}. Context}}
            child {node [taxon] {{\bf B.1}. Roles}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\subsubsection{Modality, Contingency and Theory of Mind}
\label{sect|possible-worlds}

Linked to the context representation, but seen from another angle, knowledge
representation systems may support logical \emph{modality}. A knowledge model
is logically modal if is support the concept of \emph{possible worlds}, \ie,
parallel beliefs models (or \emph{interpretations}) that can be independently
accessed.

A \emph{contingent} proposition is defined as neither always true (a tautology)
nor always false (a contradiction) in every possible world. In knowledge
representation systems for robotics that support logical modality,
interpretations are often initialised with a common set of initial beliefs
(like common-sense knowledge). This initial common knowledge is hence true in
every possible worlds for the robot, and thus does not belong to the contingent
knowledge.

Alternative mental models may be used to represent different (possibly
hypothetical or even imaginary) views on the world, from the robot own
perspective, or from persepectives of other agents, as computed by the robot.

provide explicit ways to model other point of view
on the world. This ability is often referred as the \emph{perspective taking}
ability.

@@

Since McCarthy's \emph{Situation Calculus} in 1963, numerous knowledge
representation formalisms dedicated to representation and reasoning about
actions and situation have emerged: besides situation calculs, \emph{fluent
calculus} and \emph{event calculus} are the main ones.
Thielscher~\cite{Thielscher2011} recently proposed a unification of these
approach in a new \emph{action calculus}.
